Automatic detection of bad habits of programming in Scratch

### 2014-04-17 paperFIE_en.tex
Finding section refined

\section{Findings}
\paragraph{}--Sin retocar--
The data obtained after analyzing 100 projects downloaded observations confirm that our students are also very common in community projects.
\paragraph{}--Sin retocar--Regarding the lack of habit of renaming the characters and do not use the default name assigned by the environment, the 79 \% of the projects analyzed contained at least one character without renaming the type \textit{SpriteX}.
\paragraph{}--Sin retocar--As an example to illustrate the drawbacks associated with this malpractice shown in picture \ref{fig:SpriteNaming}  a script that is difficult to read as it is necessary to explore the area to find characters which character refers to a particular block, making it difficult to debug the code before any problems or improvements and even slows own programming for the student, you should memorize or check the number of object you want to perform an action.
\begin{figure}
  \centering
    \includegraphics{img/SpriteNaming.png}
  \caption{Sprites with default names}
  \label{fig:SpriteNaming}
\end{figure}
\paragraph{}--Sin retocar--As for the repetition code, 62\% of the projects analyzed contained at least one repeated program. In fact, only 17\% of the analyzed projects made use of block \textit{def\_block} to define a block itself and can be reused in other parts of the project.

>>>>

\section{Findings}
\paragraph{}Data obtained after analyzing 100 downloaded projects confirm that observations made with our students are also very common in the community projects.
\paragraph{}Regarding the lack of habit of renaming the characters and not using the default name assigned by the environment, the 79 \% of the analyzed projects contained at least one \textit{SpriteX} character not renamed.
\paragraph{}As an example to illustrate the drawbacks associated with this malpractice, picture \ref{fig:SpriteNaming} shows a script that is difficult to read as it is necessary to explore the character area to find which character refers to a particular block, making it difficult to debug the code any problems should arise, making it hard to make any improvement in the code and even slowing down the programming time, as the name of the character must be memorized or checked every time a block is added. 
\begin{figure}
  \centering
    \includegraphics{img/SpriteNaming.png}
  \caption{Sprites with default names}
  \label{fig:SpriteNaming}
\end{figure}
\paragraph{}As for the repetition code, 62\% of the analyzed projects contained at least one repeated program. In fact, only 17\% of the analyzed projects made use of block \textit{def\_block} to define its own blocks that can be reused in other parts of the project.
